### 2016-03-08 paper/related_work.tex
yasu

FM was first introduced by Lempitsky et al. in solving an optical flow
problem~\cite{first_fusion_viktor}, where proposals

Hiroshi had a paper for doing this for binary variables but not for multilabel variables.

http://www.f.waseda.jp/hfs/CVPR2014.pdf

 This is a good idea.  Rather than having one perfect solution threads, we maintain multiple solution hypothesis which are then combined with each other.  At a high level, this strategy is similar to methods like genetic algorithms (GA) or particle swarm optimization (PSO) where multiple solutions are maintained and improved over time.

However, unlike GA or PSO where the fusion step is essentially just arbitrarily copying part of the solution, we try to find the optimal copy.

While PSO and GA have limited theoretical justification, they have been
used to produce great empirical results. For instance, in our recent
work on hand tracking, we used the particle swarm optimization
method. See Model Fitting section on page 5 of the following paper:

\url{http://research.microsoft.com/en-us/um/people/pkohli/papers/skrts_chi2015.pdf}

Also see the video here: \url{https://www.youtube.com/watch?v=R-SfOJyZlRQ&list=PLE7aZMY3Wubx6yRgP8U6GRwJCOi2Zyh2S&index=9}

Note that one may rather seek to parallelize the core optimization
libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
parallel computation. However, these algorithms need to store all the
messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
very complex and require significant engineering by experts for
modification.
%
While state-of-the-art optimization libraries are often freely available for
non-commercial purposes, most companies have to develop and maintain
in-house implementation of these optimization algorithms.

>>>>

Markov Random Field (MRF) inference has been a very active field in
Computer Vision with extensive literature. We refer the readers to
survey articles for a comprehensive
review~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
here focus our description on closely related topics.

\mysubsubsection{Fusion Move Methods}

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
used to solve challenging problems in Computer Vision such as a stereo
problem with second order smoothness priors~\cite{woodford}, a stereo
problem with parameteric surface fitting and segmentation (i.e., Surface
Stereo)~\cite{surface_stereo}, or multicut
partiioning~\cite{fusionmovesforcorrelationclustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{trw,loopy_belief_propagation}. \yasu{Pushmeet, is this
correct? Am not confident to say this?} First, FM allows us to exploit
domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces,
because the core optimization just solves a binary decision problem. In
contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.

\mysubsubsection{Parallel Fusion Methods}

\noindent There exist a few but not many parallel fusion
algorithms~\cite{viktor,olga,delong}. Lempitsky et al. introduces
parallel computation to an alpha-expansion technique, where multiple
threads simultaneously fuses mutually exclusive sets of labels. Delong
et al.~\cite{delong} and Veksler~\cite{olga} proposed an hierarchical
fusion algorithm, where labels can be simultaneously fused in a
particular order defined by a tree.

\mysubsubsection{Parallel MAP inference}

Although conceptually straightforward, we are not aware of parallel
fusion move algorithms that fuses solution proposals (as opposed to
labels) in parallel.

Note that one may rather seek to parallelize the core optimization
libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or

graph-cuts
\cite{strandmark2010parallel}

QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
parallel computation. However, these algorithms need to store all the
messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
very complex and require significant engineering by experts for
modification.
%
While state-of-the-art optimization libraries are often freely available for
non-commercial purposes, most companies have to develop and maintain
in-house implementation of these optimization algorithms.

\mysubsubsection{Genetic algorithms and Particle Swarm Optimization}

\noindent
Genetic algorithms (GA)~\cite{ga} and Particle Swarm
Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
them over time.
%
While GA and PSO have limited theoretical justification, they have been
used to produce great empirical results, for example, hand tracking via
PSO~\cite{pushmeet_hand_tracking}.  At high level, our strategy is
similar to theirs. However, unlike GA or PSO where the fusion step is
essentially just arbitrarily copying part of the solution, we 
directly optimize the objective function to find the optimal copy.
